Manuscript figures

### 2024-12-16 Manuscript_figures.Rmd
Updated `Manuscript_figures`

```{r f3g2}
plot.dat %>% 
  mutate(sex_visit_anno = paste(sex_visit, anno, sep = "_")) %$% 
  split(diff, sex_visit_anno) %>% 
  lapply(t.test)
```

@@

    pp
  }) %>% 
  cowplot::plot_grid(plotlist = ., ncol = 3) -> p
```

>>>>

```{r f3g2}
plot.dat %>% 
  mutate(sex_visit_anno = paste(sex_visit, anno, sep = "_")) %$% 
  split(diff, sex_visit_anno) %>% 
  lapply(t.test, alternative = "less")
```

@@

    pp
  }) %>% 
  cowplot::plot_grid(plotlist = ., ncol = 3)
```
